Understanding meta-analysis through data simulation with applications to power analysis

### 2023-09-11 README.Rmd
fixing typo and better structure

- `R`: contains the simulation and utility functions used in the paper and the supplementary materials
- `documents`: contains the `.Rmd` files to reproduce the paper and supplementary materials manuscripts
- `scripts`: contains the script used to produce complex objects and figures
  - `scripts\r-img.R`: create the paper figures. Figures that are not created in this script using `ggplot2` are created with the open-source program [*Inkscape*](https://inkscape.org/) and contained in the `../img/` folders.
- `objects`: contains the result of objects created by the `scripts/` scripts.

>>>>

- `R`: contains the simulation and utility functions used in the paper and the supplementary materials
- `documents`: contains the `.Rmd` files to reproduce the paper and supplementary materials manuscripts
- `scripts`: contains the script used to produce complex objects and figures
  - `scripts\r-img.R`: create the paper figures. Figures that are not created in this script using `ggplot2` are created with the open-source program [*Inkscape*](https://inkscape.org/) and contained in the `**/img/` folder.
- `objects`: contains the result of objects created by the `scripts/` scripts.

### 2023-09-11 documents/output/paper.tex
fixing typo and better structure

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/img-equal-vs-random-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/equal-effects-high-low-precision-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/random-effects-high-low-precision-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/img-metaregression-bin-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/img-metaregression-num-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/plot-meta-reg-plausible-implausible-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/plot-meta-reg-numerical-r2-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/plot-power-analysis-1}

>>>>

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/img-equal-vs-random-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/equal-effects-high-low-precision-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/random-effects-high-low-precision-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/img-metaregression-bin-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/img-metaregression-num-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/plot-meta-reg-plausible-implausible-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/plot-meta-reg-numerical-r2-1}

@@

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/user/Documents/work/shared-projects/simulating-meta-analysis/documents/output/paper_files/figure-latex/plot-power-analysis-1}
